|

### 2022-08-03 paper_comparison/paper_comparison/paper_comparison.Rmd
update graphs

add_visual_test_plot_layers <- function(p) {
  visual_dat <- polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value, prop_detect), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  boot_dat(times = 100)

  p +
  stat_smooth(data = filter(visual_dat, boot_id == 1), geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "Visual"), 
              method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 1) +
  stat_smooth(data = visual_dat, geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "Visual"), 
              method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 0.05) +
  geom_point(data = filter(visual_dat, boot_id == 1), aes(log(effect_size), prop_detect), alpha = 0.1)

}

@@

```{r eval = FALSE}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(dd = first(abs(log(effect_size) - 5)), p_value = first(p_value)) %>%
  arrange(dd)

@@

```{r power-overview, fig.height=7.5, fig.cap="Power overview. \\label{fig:power-overview}"}
conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_SW_conv_test_plot_layers() %>%
  add_visual_test_plot_layers() +
  geom_vline(xintercept = 2, linetype = 2) + 
  geom_vline(xintercept = 3, linetype = 2) +
  geom_vline(xintercept = 4, linetype = 2) +
  geom_vline(xintercept = 5, linetype = 2) -> base_plot

@@

VI_MODEL$plot_lineup(polynomials_lineup$lineup_364$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) %~~% 3~", F-test p-value" == .(format(filter(polynomials, lineup_id == 364)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 364)$p_value[1], digits = 3)))) -> bottom_plot_2

VI_MODEL$plot_lineup(polynomials_lineup$lineup_574$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) %~~% 4~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 574)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 574)$p_value[1], digits = 3)))) -> bottom_plot_3

VI_MODEL$plot_lineup(polynomials_lineup$lineup_179$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) %~~% 5~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 179)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 179)$p_value[1], digits = 3)))) -> bottom_plot_4

@@

>>>>

add_visual_test_plot_layers <- function(p, points = c()) {
  visual_dat <- polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value, prop_detect), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  boot_dat(times = 100)

  p +
  stat_smooth(data = filter(visual_dat, boot_id == 1), geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "Visual"), 
              method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 1) +
  stat_smooth(data = visual_dat, geom = "line", 
              aes(log(effect_size), reject, group = boot_id, col = "Visual"), 
              method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 0.05) +
  geom_point(data = filter(visual_dat, boot_id == 1), aes(log(effect_size), prop_detect), alpha = 0.1) + 
  geom_point(data = filter(visual_dat, boot_id == 1, lineup_id %in% points), aes(log(effect_size), prop_detect), alpha = 1, col = "red", size = 2)
}

@@

```{r eval = FALSE}
filter(polynomials, set == 123)

polynomials %>%
  group_by(lineup_id) %>%
  summarise(dd = first(abs(log(effect_size) - 5)), p_value = first(p_value), prop_detect = first(prop_detect)) %>%
  arrange(dd) %>%
  head(30) %>%
  summarise(tt = median(prop_detect))

@@

```{r power-overview, fig.height=7.5, fig.cap="Power overview. \\label{fig:power-overview}"}
conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_SW_conv_test_plot_layers() %>%
  add_visual_test_plot_layers(points = c(415, 131, 322, 378)) +
  geom_vline(xintercept = 2, linetype = 2) + 
  geom_vline(xintercept = 3, linetype = 2) +
  geom_vline(xintercept = 4, linetype = 2) +
  geom_vline(xintercept = 5, linetype = 2) -> base_plot

@@

VI_MODEL$plot_lineup(polynomials_lineup$lineup_131$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) %~~% 3~", F-test p-value" == .(format(filter(polynomials, lineup_id == 131)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 131)$p_value[1], digits = 3)))) -> bottom_plot_2

VI_MODEL$plot_lineup(polynomials_lineup$lineup_322$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) %~~% 4~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 322)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 322)$p_value[1], digits = 3)))) -> bottom_plot_3

VI_MODEL$plot_lineup(polynomials_lineup$lineup_378$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) %~~% 5~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 378)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 378)$p_value[1], digits = 3)))) -> bottom_plot_4

@@

```{r}
conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_SW_conv_test_plot_layers() %>%
  add_visual_test_plot_layers() +
  geom_vline(xintercept = 2, linetype = 2) + 
  geom_vline(xintercept = 3, linetype = 2) +
  geom_vline(xintercept = 4, linetype = 2) +
  geom_vline(xintercept = 5, linetype = 2) +
  facet_wrap(~x_dist)
```

```{r}
conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_SW_conv_test_plot_layers() %>%
  add_visual_test_plot_layers() +
  geom_vline(xintercept = 2, linetype = 2) + 
  geom_vline(xintercept = 3, linetype = 2) +
  geom_vline(xintercept = 4, linetype = 2) +
  geom_vline(xintercept = 5, linetype = 2) +
  facet_wrap(~shape)
```
